---
title: "Assignment 2 SQL and R"
author: "[Kleber Perez - `r format(Sys.Date(), '%B %d, %Y')`](https://www.linkedin.com/in/kleberperez/)" 
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("RMySQL")
# 1. Library
library(RMySQL)

```

## DBMS Connection Using MySQL

> Choose six recent popular movies.  Ask at least five people that you know (friends, family, classmates, imaginary friends) to rate each of these movie that they have seen on a scale of 1 to 5.  Take the results (observations) and store them in a SQL database.  Load the information into an R dataframe.

```{r}
# 2. Settings
db_user <- 'root'
db_password <- ''
db_name <- 'MovieDB'
db_host <- '127.0.0.1' # localhost for local access
db_port <- 3306

# 3. Read data from db
mydb <-  dbConnect(MySQL(), user = db_user, password = db_password,
                 dbname = db_name, host = db_host, port = db_port)
s <- paste0("SELECT v.*, r.User, r.Rating FROM Movies v INNER JOIN Rating r ON v.Id = r.MovieId;")
rs <- dbSendQuery(mydb, s)
df <-  fetch(rs, n = -1)
df
on.exit(dbDisconnect(mydb))

```

## Summary

```{r df}
summary(df)
```

## Including Plots

```{r, echo=FALSE}
f <- as.factor(df$Title)
levels(f)
plot(f, df$Rating)
```

<br />

> Deliverables should include your SQL scripts and your R Markdown code, posted to GitHub. 

> This is by design a very open ended assignment.  A variety of reasonable approaches are acceptable.  You can (and should) blank out your SQL password if your solution requires it; otherwise, full credit requires that your code is 'reproducible', with the assumption that I have the same database server and R software.  

<br />
<br />
<br />
<br />

> *Please email to: * <a href="mailto:kleber.perez@live.com">kleber.perez@live.com</a> *for any suggestion.*

<footer class="border-top text-muted fixed-bottom">

        Data 607 Assignment #2 - MSDS 2019 Program.

</footer>

\textbf{Text ignored: END of other links}



